---
title: "QMM ASSIGNMENT 2"
author: "Goli Sai Priyanka"
date: "2023-09-24"
output:
  pdf_document: default
  html_document: default
---
The Weigelt Corporation has three branch plants with excess production capacity. Fortunately,
the corporation has a new product ready to begin production, and all three plants have this
capability, so some of the excess capacity can be used in this way. This product can be made in
three sizes--large, medium, and small--that yield a net unit profit of $420, $360, and $300,
respectively. Plants 1, 2, and 3 have the excess capacity to produce 750, 900, and 450 units per
day of this product, respectively, regardless of the size or combination of sizes involved.
The amount of available in-process storage space also imposes a limitation on the production
rates of the new product. Plants 1, 2, and 3 have 13,000, 12,000, and 5,000 square feet,
respectively, of in-process storage space available for a day's production of this product. Each
unit of the large, medium, and small sizes produced per day requires 20, 15, and 12 square feet,
respectively.
Sales forecasts indicate that if available, 900, 1,200, and 750 units of the large, medium, and
small sizes, respectively, would be sold per day.
At each plant, some employees will need to be laid off unless most of the plant’s excess
production capacity can be used to produce the new product. To avoid layoffs if possible,
management has decided that the plants should use the same percentage of their excess capacity
to produce the new product.
Management wishes to know how much of each of the sizes should be produced by each of the
plants to maximize profit.
Solve the problem using lpsolve, or any other equivalent library in R.
Requirements
All due dates are included in the Assignment Schedule.

#solution : 
The objective function is Max Z = 420(K1 + S2 + U3) + 360(K1 + S2 + U3) + 300(K1 + S2 + U3)
Rearraning the objective function Max Z = 420K1+360S1+300U1+420K2+360S2+300U2+420K3+360S3+300U3
subject to Constrains

$$K1 + S1 + U1 \le 750$$
$$K2 + S2 + U2 \le 900$$
$$K3 + S3 + U3 \le 450$$


$$20K1 + 15S1 + 12U1 \le 13000$$

$$20K2 + 15S2 + 12U2 \le 12000$$
$$20K3 + 15S3 + 12U3 \le 5000$$
$$K1 + K2 + K3\le 900$$
$$S1 + S2 + S3 \le 1200$$
$$U1 + U2 + U3 \le 750$$
Non negativity constraints
$$K1, K2, K3, S1, S2, S3, U1, U2, U3 \ge 0$$

$$900K1 + 900S1 + 900U1 − 750K2 − 750S2 − 750U2 + 0K3 + 0S3 + 0U3 = 0$$
$$0K1 + 0S1 + 0U1 + 450K2 + 450S2 + 450U2 − 900K3 − 900S3 − 900U3 = 0$$
$$450K1 + 450S1 + 450U1 + 0K2 + 0S2 + 0U2 − 750K3 − 750S3 − 750U3 = 0$$
##SOLUTION :
Now, let’s solve this problem using R.

To solve the this problem we need to use the library “lpsolve
```{r}
library(lpSolve)
z <- c(420,360,300,420,360,300,420,360,300)
constrains <- matrix(c(1,1,1,0,0,0,0,0,0,
0,0,0,1,1,1,0,0,0,
0,0,0,0,0,0,1,1,1,
20,15,12,0,0,0,0,0,0,
0,0,0,20,15,12,0,0,0,
0,0,0,0,0,0,20,15,12,
1,0,0,1,0,0,1,0,0,
0,1,0,0,1,0,0,1,0,
0,0,1,0,0,1,0,0,1,
900,900,900,-750,-750,-750,0,0,0,
0,0,0,450,450,450,-900,-900,-900,
450,450,450,0,0,0,-750,-750,-750),nrow = 12,byrow = TRUE)

constrains


directions <- c("<=",
"<=",
"<=",
"<=",
"<=",
"<=",
"<=",
"<=",
"<=",
"=",
"=",
"=")



RHS <- c(750,
900,
450,
13000,
12000,
5000,
900,
1200,
750,
0,
0,
0)


maximum <- lp("max",z,constrains,directions,RHS)
maximum

```


```{r}
maximum$solution

```


```{r}
maximum$solution[1]
```



```{r}
maximum$solution[2]
```


```{r}
maximum$solution[3]
```


```{r}
maximum$solution[4]
```


```{r}
maximum$solution[5]
```


```{r}
maximum$solution[6]
```


```{r}
maximum$solution[7]
```


```{r}
maximum$solution[8]
```


```{r}
maximum$solution[9]
```
